### 2015-05-05 Workshop2015/camera-ready/relwork.tex
version à 6 pages

In the cloud, the   SLA's rely on two principles: (i)  negotiation of conditions in which services will be provided and that are statically agreed between the parts and (ii)  monitoring of these conditions during the use of cloud resources in order to detect SLA contract violation.

@@

%Negotiating a SLA may be a difficult task.
%Indeed, 
SLA's are normally expressed in terms of \textit{technical}, quantifiable measures, like the storage space size, the degree of virtualization, the number of requests for a given service. 
From the user point of view, the interest is normally on \textit{service} delivery measures that are related with her QoS requirements like service availability, resilience, recovery time or cost.
The challenge is to couple technical and service delivery measures expressed in SLA's in order to agree on the conditions in which they will be considered for executing tasks for a user. Existing works use matching and negotiation techniques for addressing this challenge.  
For instance,~\cite{5547150} 
proposes a bottom-up approach based on a cloud component that monitors technical measures, analyses and matches them to service delivery (high level) clauses expressed by the user.
  \cite{Dastjerdi:2012:DOA:2275356.2275360} describes a \textit{Semantic SLA} that can be understood by all parties including providers, consumers, and monitoring services.
Their goal is, starting from a high level SLA, to measure and identify how to derive SLA measures  at different layers of the cloud.  \cite{Ortiz:2013:VPS:2486767.2486772}
  proposes a set of templates to  cloud data services users, each specifying the query type that can be executed with some tread-off in time and corresponding cost.  The client  chooses among the proposed templates the one that best corresponds   to her requirements. \cite{6141307} proposes a set of matching algorithms to identify compatible cloud providers for a given requirements specification by matching SLA parameters. Cloud SLA parameters and application requirements are represented by two models using RDF. RDF definitions are then converted into graph representations. An Induced Propagation Graph is calculated using both models to establish a correspondence between them.

@@

Recent  works on SLA are devoted to extend  SLA specifications for including  security concerns. 
\cite{6274042} propose an extension of the WSAgreement, initially developed by the GRAAP
working group. 
Security constraints are expressed over the service description
terms (SDTs) and the service level objectives (SLOs) of the SLA. 
This leads to an interoperable security expression that can be used by users for comparing security levels of different cloud  providers. Hale and Al. in \cite{6655684} extend their first work proposing an ontology representation of security concerns and connect security services expressed in SLA  to documents regulating security controls.
\cite{LunaGarcia:2012:BCS:2381913.2381932} focuses on how to build a SEcSLA Template starting from gathering then categorizing a set of security statements using a semantic tool. 
The designed template is then used both to express user security requirements and cloud service provider security provision.
Finally, some works  deal with SLA violation anticipation and SLA failure cascading on violation detection.  \cite{Dastjerdi:2012:DOA:2275356.2275360}  proposes an SLA dependency model using Web Service Modeling Ontology (WSMO) to build a knowledge database. \cite{5614035} proposes to anticipate failure by analyzing the monitored feature. 
\cite{5614035} proposes LAYSI, a layered solution that minimizes user interactions with the system and prevents violations of agreed SLAs.

 Recent work on SLA modeling in the cloud does not seem to use SLA for data integration, maybe because measures concern data services and not data itself.
Furthermore, SLA are in general exclusively used in a mono-cloud context to express the conditions in which a user can expect the cloud to provide resources. Whereas data integration in a multi-cloud context implies to express and enforce multiple granularity constraints at different levels of SLA (users, services, clouds and inter-cloud environments).  Finally,  an a-priori SLA enforcement mechanism -in opposition to the a-posteriori SLA monitoring to detect violation-  is mandatory to assess data integration feasibility. \cite{anisetti2014auctions} proposed an e-auctions based approach for matching services with requirements in multi-cloud settings. Our work aims at going further in the use of SLA for integrating data and it provides strategies to guide the whole data integration process.

>>>>

The use of cloud SLA rely on two principles: (i)  negotiation of conditions in which services will be provided and that are statically agreed between the parts and (ii)  monitoring of these conditions during the use of cloud resources in order to detect SLA contract violation.

@@

%Negotiating a SLA may be a difficult task.
%Indeed, 
SLA are normally expressed in terms of \textit{technical}, quantifiable measures, like the storage space size, the degree of virtualization, the number of requests for a given service. 
From the user point of view, the interest is normally on \textit{service} delivery measures that are related with her QoS requirements like service availability, resilience, recovery time or cost.
The challenge is to couple technical and service delivery measures expressed in SLA in order to agree on the conditions in which they will be considered for executing tasks for a user. Existing works use matching and negotiation techniques for addressing this challenge.  
For instance,~\cite{5547150} 
proposes a bottom-up approach based on a cloud component that monitors technical measures, analyses and matches them to service delivery (high level) clauses expressed by the user.
\cite{Dastjerdi:2012:DOA:2275356.2275360} describes a \textit{Semantic SLA} that can be understood by all parties including providers, consumers, and monitoring services.
Their goal is, starting from a high level SLA, to measure and identify how to derive SLA measures  at different layers of the cloud.  
\cite{Ortiz:2013:VPS:2486767.2486772} proposes a set of templates to cloud users, each specifying the query type that can be executed with their tread-off in time and cost.  
The client  chooses among the proposed templates the one that best corresponds   to her requirements. \cite{6141307} proposes a set of matching algorithms to identify compatible cloud providers for a given requirements specification by matching SLA parameters, represented in RDF. RDF definitions are then converted into graph representations. An \textit{Induced Propagation Graph} is calculated from both models to establish correspondences.

@@

Recent  works on SLA are devoted to extend  SLA specifications to include  security concerns. 
\cite{6274042} propose an extension of the WSAgreement, initially developed by the GRAAP
working group. 
Security constraints are expressed over the service description
terms (SDTs) and the service level objectives (SLOs) of the SLA. 
This leads to an interoperable security expression that can be used by users for comparing security levels of cloud  providers. 
Hale and Al. in \cite{6655684} extend their first work proposing an ontology representation of security concerns and connect security services expressed in SLA  to documents regulating security controls.
\cite{LunaGarcia:2012:BCS:2381913.2381932} focuses on how to build a SEcSLA template starting from gathering then categorizing a set of security statements using a semantic tool. 
The designed template is then used both to express user security requirements and cloud service provider security provision.
Finally, some works  deal with SLA violation anticipation and SLA failure cascading on violation detection.  \cite{Dastjerdi:2012:DOA:2275356.2275360}  proposes an SLA dependency model using Web Service Modeling Ontology (WSMO) to build a knowledge database. 
\cite{5614035} proposes to anticipate failure by analyzing the monitored feature. 
\cite{5614035} proposes LAYSI, a layered solution that minimizes user interactions with the system and prevents violations of agreed SLAs.

 Recent work on SLA modeling in the cloud does not seem to use SLA for data integration, maybe because measures concern data services and not data itself.
Furthermore, SLA are in general exclusively used in a mono-cloud context to express the conditions in which a user can expect the cloud to provide resources, whereas data integration in a multi-cloud context implies to express and enforce multiple granularity constraints at different levels of SLA (users, services, clouds and inter-cloud environments).  
Finally,  an a-priori SLA enforcement mechanism -in opposition to the a-posteriori SLA monitoring to detect violation-  is mandatory to assess data integration feasibility. 
\cite{anisetti2014auctions} proposed an e-auctions based approach for matching services with requirements in multi-cloud settings. 
Our work aims at going further in the use of SLA for integrating data and it provides strategies to guide the whole data integration process.
